\chapter*{Foreword}
This dissertation summarizes the work that I conducted at \textit{Robotics, Autonomous System and Control} (RAC) group of Siemens Corporate Technology (CT). I gratefully acknowledge the generous financial support of Siemens AG.

First of all, I would like to thank my doctoral supervisor, Dr.~Georg von Wichert, for your supervision and tremendous support during my entire Ph.D. work. You let me find my research direction and makes me believe in myself. Several times, you generously sacrifice your private time to help me revise my paper until the midnight. I really feel so lucky to be your student. I also would like to thank Prof.~Dr.~-Ing./Univ.~Martin Buss, who gives me the opportunity to finish and defend my thesis at Institute of Automatic
 Control Engineering of TU~M\"unchen. I also sincerely thank Dr.~Gisbert Lawitzky, who provides me the chance to work in this team and `SIR', an amazing mobile manipulation robot which accompanies me during the past joyful years. 

I would like to thank every member in the RAC team. Their specializations in each domain of robotics provide me a broad view of the fantastic world of robotics as well as enlighten me in many aspects of my research work. I enjoy every lunch, every coffee round and every `Mannerabend' with them. Special thanks go to  Ziyuan Liu, Vincent Dietrich, Bernd Kast, Florian Wirnshofer, Philip Koehler, Philipp Schmitt and Konstantin Ritt, for their fruitful discussions, critical reviews on each paper and great contributions to this dissertation. I am so happy to meet these amazing people in my life and enjoy every moment of solving challenging technical problems with them. Great thanks also go to Dr.~Thomas W\"osch, Dr.~Wendelin Feiten and Dr.~Kai Wurm for their immense experience, invaluable advice, and technical support. 

Finally, I would like to thank my wife Zijia Bai and my parents, who take care of my little son, give me unconditional love, endless patience and enormous encouragement. Any word can not be enough to express my gratitude to them.

I wish all the best to all of them.    

\vspace{1cm}
\noindent
Munich, December 2016 \hfill Dong Chen

